Effects of Reynolds Number on the Performance and Near-Wake Dynamics of a Vertical-Axis Cross-Flow Turbine

### 2015-06-30 paper.tex
Resize figures and remove titles for differing quantities; resolves #22 and #28

\begin{figure}[ht!]
\centering
\includegraphics[width=0.95\textwidth]{figures/all_foils_re_dep}
\caption{Foil section characteristics computed by XFOIL for various $Re_c$.}
\label{fig:foil-Re-dep}
\end{figure}

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=0.95\textwidth]{figures/foil_kinematics_ct}
\caption{Geometric angle of attack (a), relative velocity (b) and torque coefficient
(c) calculated with a NACA 0020 foil.}
\label{fig:blade-kinematics}
\end{figure}

>>>>

\begin{figure}[ht!]
\centering
\includegraphics[width=0.9\textwidth]{figures/all_foils_re_dep}
\caption{Foil section characteristics computed by XFOIL for various $Re_c$.}
\label{fig:foil-Re-dep}
\end{figure}

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=0.9\textwidth]{figures/foil_kinematics_ct}
\caption{Geometric angle of attack, relative velocity and torque coefficient
calculated with a NACA 0020 foil.}
\label{fig:blade-kinematics}
\end{figure}
